`gosset`: An R package for analysis and synthesis of ranking data in agricultural

### 2022-06-24 inst/paper/paper.Rmd
Update paper.Rmd

The `nicabean` is a list with two data frames: i) `trial`, contains the trial data with farmers' evaluations, ranked from 1 to 3, with 1 being the higher ranked variety and 3 the lowest ranked variety for the given trait and incomplete block; ii) `covar`, contains the covariates associated to the on-farm trial plots and farmers. This example will require the packages PlackettLuce [@Turner2020], climatrends [@climatrends], nasapower [@nasapower] and ggplot2 [@ggplot2].

``` {r, message = FALSE, eval = TRUE, echo = TRUE}
library("gosset")
library("PlackettLuce")
library("climatrends")
library("nasapower")
library("ggplot2")

@@

To consider the effect of climate factors on variety performance, we used climatic covariates to fit a 
Plackett-Luce tree. For brevity, we used the variables maximum nighttime temperature (maxNT) and  maximum daytime temperature, but more variables can be used in a Plackett-Luce tree. Temperature data were obtained from the AgERA5 dataset, using the R package *ag5Tools* [@ag5tools]. The temperature data downloaded from NASA POWER were used for computing the climatic variables with the package *climatrends* [@climatrends]. In this case, we only use the rankings corresponding to the overall performance of varieties.

>>>>

The `nicabean` is a list with two data frames: i) `trial`, contains the trial data with farmers' evaluations, ranked from 1 to 3, with 1 being the higher ranked variety and 3 the lowest ranked variety for the given trait and incomplete block; ii) `covar`, contains the covariates associated to the on-farm trial plots and farmers. This example will require the packages PlackettLuce [@Turner2020], climatrends [@climatrends], and ggplot2 [@ggplot2].

``` {r, message = FALSE, eval = TRUE, echo = TRUE}
library("gosset")
library("PlackettLuce")
library("climatrends")
library("ggplot2")

@@

To consider the effect of climate factors on variety performance, we used climatic covariates to fit a 
Plackett-Luce tree. For brevity, we used the variables maximum nighttime temperature (maxNT) and  maximum daytime temperature, but more variables can be used in a Plackett-Luce tree. Temperature data were obtained from the AgERA5 dataset, using the R package *ag5Tools* [@ag5tools]. The temperature data downloaded from AgERA5 were used for computing the climatic variables with the package *climatrends* [@climatrends]. In this case, we only use the rankings corresponding to the overall performance of varieties.
